---
title: "Homework 2 Original Code"
author: "Mel Zarate"
date: "9/25/2019"
output: html_document
---
#Homework 2

This is my first code for Homework 2. The homework states: 

"Every Saturday morning, at the same time, a primatologist goes and sits in the forest to listen for titi monkey calls, counting the number of calls they hear in a 2 hour window from 5am to 7am. Based on previous knowledge, she believes that the mean number of calls she will hear in that time is exactly 15. Let X represent the appropriate Poisson random variable of the number of calls heard in each monitoring session."

For the Poisson distribution, x=8 and lambda=15. To find the probability that 8 calls will be heard, I will use the dpois() function (thanks google): 

```{r}
dpois(x=8, lambda = 15)
```

Comment: I got something a little different. I think for this you need to get the cumulative probability of getting every number above 8. So that means you have to add the probability of getting 9,10,11,12,13,14,15,... Also, it does not stop at 15, it goes to infinity. I did 1-(probability of getting 1-8 calls)

And I'll repeat this method for finding the probability that there are no calls. 

```{r}
dpois(x=0, lambda = 15)
```
Super small, makes sense! 

Comment: Got the same.

three calls? 
```{r}
dpois(x=3, lambda = 15)
```

comment: I got something differnet here but I am not 100% confident in my answer. I also got a small number.

Plot the relevant Poisson mass function over the values in range 0 ≤ x ≤ 30.

```{r}
x <- 0:30
l = 15
probset<-dpois(x=x,lambda=l)
barplot(probset,names.arg=x,space=0,xlab="x",ylab="Pr(X = x)",main="Probability Mass Function")
```

Comment: Looks good to me!

Simulate 104 results from this distribution (i.e., 2 years of Saturday monitoring sessions). For this, I believe we'd use the rpois() function. 

```{r}
rpois(x = 104, lambda = 15) #x is the number of times we are simulating it, lambda, again is the assumed average
```
Ok that didn't work.. *continues googling*

I'm going to try to set the variables before using rpois():

```{r}
x <- 104
l = 15
rpois(x,l)
```
Got it! now to plot these...

Comment: I think you nailed it! Mine is the same.

Plot the simulated results using hist() and use xlim() to set the horizontal limits to be from 0 to 30. How does your histogram compare to the shape of the probability mass function you plotted above?

```{r}
library(ggplot2)
hist(rpois(x,l), 
  main = "Observed Call Frequency",
  xlab = "Number of Calls",
  xlim = c(0,30)
)
```
Compared to the earlier plot, we don't have any instances of less than ~6 or more than ~24 calls. 

Comment: Did mine slightly different but same result more or less.

#Challenges

1. The fact that this was supposed to be a Poisson distribution threw me off a bit, and I had to do some googling to see how to find the probability of an event given a mean in this distribution. I'm still a little confused by the difference between Poisson and normal distributions. 

Comment: Yes, that took me a bit to figure out as well. My understanding is that they are similar types of binomial distribution but the main difference is that aproximation on the tails of a poisson distribution are more accurate.

2. The same is true with bootstrapping- in class, we had discussed bootstrapping as take a subset of a sample a certain number of times and working with those means, and here we were just choosing one observation session 104 times. I had to work out the differences in doing so. 

Comment:Not sure where bootstrapping comes into play here. Must be something I missed since I wasn't in class.

3. I had to mess around with the rpois() code to figure out how to set x as the number of simulations and lambda as the average.  

Comment: Took a little bit of fiddling around for me too. Seems like you found an effective syntax.

Plotting challenges: 

4. xlim() is a ggplot function?? I thought it was a built in function. 

Comment: Its actually both

5. I had to re-organize the code a few times, mainly because of missing commas and/or parentheses. 

Comment: Typos are a pain. Overall, this looks fantastic (in my humble opinion of course). Great Job Mel, and welcome back!!!!

