---
title: "Homework 2 Original Code"
author: "Mel Zarate"
date: "9/25/2019"
output: html_document
---
#Homework 2

This is my first code for Homework 2. The homework states: 

"Every Saturday morning, at the same time, a primatologist goes and sits in the forest to listen for titi monkey calls, counting the number of calls they hear in a 2 hour window from 5am to 7am. Based on previous knowledge, she believes that the mean number of calls she will hear in that time is exactly 15. Let X represent the appropriate Poisson random variable of the number of calls heard in each monitoring session."

For the Poisson distribution, x=8 and lambda=15. To find the probability that 8 calls will be heard, I will use the dpois() function (thanks google): 

```{r}
dpois(x=8, lambda = 15)
```

And I'll repeat this method for finding the probability that there are no calls. 

```{r}
dpois(x=0, lambda = 15)
```
Super small, makes sense! 


three calls? 
```{r}
dpois(x=3, lambda = 15)
```

Plot the relevant Poisson mass function over the values in range 0 ≤ x ≤ 30.

```{r}
x <- 0:30
l = 15
probset<-dpois(x=x,lambda=l)
barplot(probset,names.arg=x,space=0,xlab="x",ylab="Pr(X = x)",main="Probability Mass Function")
```

Simulate 104 results from this distribution (i.e., 2 years of Saturday monitoring sessions). For this, I believe we'd use the rpois() function. 

```{r}
rpois(x = 104, lambda = 15) #x is the number of times we are simulating it, lambda, again is the assumed average
```
Ok that didn't work.. *continues googling*

I'm going to try to set the variables before using rpois():

```{r}
x <- 104
l = 15
rpois(x,l)
```
Got it! now to plot these...

Plot the simulated results using hist() and use xlim() to set the horizontal limits to be from 0 to 30. How does your histogram compare to the shape of the probability mass function you plotted above?

```{r}
library(ggplot2)
hist(rpois(x,l), 
  main = "Observed Call Frequency",
  xlab = "Number of Calls",
  xlim = c(0,30)
)
```
Compared to the earlier plot, we don't have any instances of less than ~6 or more than ~24 calls. 

#Challenges

1. The fact that this was supposed to be a Poisson distribution threw me off a bit, and I had to do some googling to see how to find the probability of an event given a mean in this distribution. I'm still a little confused by the difference between Poisson and normal distributions. 

*Hi! Samesies! I definitely was doing a lot of youtubing and googling, which helped, but still confused about when to use which of the functions dpois or ppois. Hopefully, with enough of us having these same questions, we will go over this in class, especially as it seems like something we will be using as primatologists!*

2. The same is true with bootstrapping- in class, we had discussed bootstrapping as take a subset of a sample a certain number of times and working with those means, and here we were just choosing one observation session 104 times. I had to work out the differences in doing so. 

*Right! I agree. This turned out to be much easier than I thought it would be once I saw what the rpois() function could do.*

3. I had to mess around with the rpois() code to figure out how to set x as the number of simulations and lambda as the average.  

*Yep, in this case, google was once again my friend!*

Plotting challenges: 

4. xlim() is a ggplot function?? I thought it was a built in function. 

*I also had so many issues with setting this and all of the other plot constraints/settings/labels. I finally got it to work but felt like I was just patching it together until it worked. I did not know that it was a ggplot function either! We should ask Christ to clarify this and maybe go over some examples?*

5. I had to re-organize the code a few times, mainly because of missing commas and/or parentheses. 

*Yep! Me too!! Once I got it, it looked okay, but I felt like I still have a lot to learn about streamlining code and making it neat.*

*Overall, your code and annotations look great and really helped me follow your process and how you overcame challenges!*